Preferences interact: what consequences for a Schelling scenario?

### 2019-11-07 ethnic_value_rum.Rmd
Add files via upload

raw_f <- rbind(eq_30,eq_10,mj_30,mj_10)

@@

eq_30_10 %>% filter(e_sqr == 30, v_crl == 10)
mj_30_10 %>% filter(e_sqr == 30, v_crl == 10)

>>>>

test <- read.csv("test-beta-eth.csv",sep = ",",skip = 6)
names(test)[names(test) == "X.step."] <- "step"
names(test)[names(test) == "X.run.number."] <- "run"
names(test)[names(test) == "beta.ie"] <- "beta_ie"
names(test)[names(test) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself...of.turtles.with..count..turtles.on.neighbors.....1."] <- "eth_seg"

raw_f <- rbind(eq_30,eq_10,mj_30,mj_10,eq_30_10,mj_30_10)

@@

raw_f %>% filter(e_sqr == 30, v_crl == 10)
